Incentivizing Exploration by Heterogeneous Users

### 2018-06-05 algorithm_payment.tex
there was not a calculation error after all

Thus, for any $s \geq \EvenLaterPhase$,
the \Kth{s} pull of arm $i$ is incentivized  
with probability at most
$24 \ARMNUM d \cdot \exp \left(
- \frac{1.8 s}{\pfedit{64} \Diam^2 d^2 \sigma^2}
  \cdot \min(\TieCutoff, \frac{\MinProb}{\TieDensity})^2
\right)$.
Summing over all arms and phases $s$,
adding the at most $\ARMNUM \EvenLaterPhase$ incentivizations in
the first \EvenLaterPhase phases, 
and using that $\exp(-x) \leq 1-x/2$ for $x \leq 1$,
the expected total number of arm incentivizations is at most
\begin{align*}
\lefteqn{\ARMNUM \EvenLaterPhase
  + 24 \ARMNUM^2 d \cdot \frac{1}{1 - \exp \left(
- \frac{1.8}{\pfedit{64} \Diam^2 d^2 \sigma^2}
  \cdot \min(\TieCutoff, \frac{\MinProb}{\TieDensity})^2
  \right)}}
\\ & = O\left( \max \left(
     \frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3},
\frac{\ARMNUM \Diam^3 d^3 \sigma^3}{\TieCutoff^3},
     \ARMNUM \exp \left(\frac{2}{\MinProb} \right) \right)
+ \max \left(
     \frac{\ARMNUM^2 d^3 \TieDensity^2 \sigma^2 \Diam^2}{\MinProb^2},
\frac{\ARMNUM^2 d^3 \sigma^2 \Diam^2}{\TieCutoff^2}
\right) \right)
\\ & = O\left( \ARMNUM \exp \left(\frac{2}{\MinProb}\right) \right).
\end{align*}

>>>>

Thus, for any $s \geq \EvenLaterPhase$,
the \Kth{s} pull of arm $i$ is incentivized  
with probability at most
$24 \ARMNUM d \cdot \exp \left(
- \frac{1.8 s}{256 \Diam^2 d^2 \sigma^2}
  \cdot \min(\TieCutoff, \frac{\MinProb}{\TieDensity})^2
\right)$.
Summing over all arms and phases $s$,
adding the at most $\ARMNUM \EvenLaterPhase$ incentivizations in
the first \EvenLaterPhase phases, 
and using that $\exp(-x) \leq 1-x/2$ for $x \leq 1$,
the expected total number of arm incentivizations is at most
\begin{align*}
\lefteqn{\ARMNUM \EvenLaterPhase
  + 24 \ARMNUM^2 d \cdot \frac{1}{1 - \exp \left(
- \frac{1.8}{256 \Diam^2 d^2 \sigma^2}
  \cdot \min(\TieCutoff, \frac{\MinProb}{\TieDensity})^2
  \right)}}
\\ & = O\left( \max \left(
     \frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3},
\frac{\ARMNUM \Diam^3 d^3 \sigma^3}{\TieCutoff^3},
     \ARMNUM \exp \left(\frac{2}{\MinProb} \right) \right)
+ \max \left(
     \frac{\ARMNUM^2 d^3 \TieDensity^2 \sigma^2 \Diam^2}{\MinProb^2},
\frac{\ARMNUM^2 d^3 \sigma^2 \Diam^2}{\TieCutoff^2}
\right) \right)
\\ & = O\left( \ARMNUM \exp \left(\frac{2}{\MinProb}\right) \right).
\end{align*}
